Circumnuclear Media and Accretion Rates of Quiescent Supermassive Black Holes

### 2015-03-07 ms.tex
we dont believe you2

\begin{table*}
\begin{threeparttable}
%\centering
\begin{minipage}{18cm}
\caption{Definitions of commonly used variables}
\begin{tabular}{ll}
\hline
{Variable} & {Definition} \\
\hline
$M_{\bullet}$ & Black hole mass \\
$\tilde{v}_{w}$ & Total heating parameter, including minimum heating rate from stellar velocity dispersion \\
$v_{w}$ & Total heating parameter, excluding heating rate from stellar velocity dispersion \\
$r_{s}$ & Stagnation radius (where radial velocity goes to zero) \\
$r_{\rm soi}$ & radius of sphere of influence (eq.~[\ref{eq:rsoi}]) \\
$r_{\rm b}$ & outer break radius of stellar density profile \\ 
$r_{\rm Ia}$ & radius exterior to which Ia SN are infrequent compared to the dynamical/inflow timescale (eq.~[\ref{eq:rIa}]) \\ 
$\rho_{\star}(r)$ & 3D radial stellar density profile \\
$\rho(r)$ & gas density of CNM \\
$M_{\star}(r)$ & total enclosed stellar mass inside radius $r$ \\
$M_{\rm enc}(r)$ & total encolsed mass inside radius $r$ (SMBH + stars) \\
$q(r)$ & mass source term due to stellar winds (eq.~[\ref{eq:q}]) \\
$\eta$ & parameter setting normalization of mass input from stellar winds (eq.~[\ref{eq:q}]) \\
$\tau_{\star}$ & age of stellar population, in case of a single burst of star formation \\
$\Gamma$ & power-law slope of radial stellar density profile interior to the break radius \\
$\sigma(r)$ & stellar velocity dispersion \\
$\dot{M}$ & mass accretion rate \\
$\dot{M}_{\rm Ia}$ & maximum mass accretion rate as limited by SN Ia blow-out (eq.~[\ref{eq:eddr_Ia}]) \\
$\dot{M}_{\rm C}$ & equilibrium accretion rate set by Compton heating (eq.~[\ref{eq:MdotC}]) \\
$\dot{M}_{\rm TI}$ & maximum accretion rate for thermally stable accretion (eq.~[\ref{eq:Mdotmax}]) \\
$\dot{q}_{\rm heat}/|\dot{q}_{\rm rad}|$ & ratio of external heating (stellar winds, SN Ia, MSPs) to radiative cooling (eq.~[\ref{eq:cooling2}]) \\
$t_{\rm h}$ & Hubble timescale \\
\hline
\label{table:definitions}  
\end{tabular}
\begin{tablenotes}
\item{$^{(a)}FILL IN$}
\end{tablenotes}
\end{minipage}
\end{threeparttable}

@@

Our analytic derviations neglect the effects of heat conduction, an assumption we now check.  The ratio of the magnitude of the conductive heating rate (eq.~[\ref{eq:qdotcond}]) to the external heating rate at the stagnation radius is given by
\begin{align}
  \left.\frac{\nabla\cdot(\kappa \nabla T)}{q v_{\rm
w}^{2}/2}\right|_{r_{\rm s}} &\sim \frac{2t_{\rm h}\kappa_0
T|_{r_{\rm s}}^{7/2}}{r_{\rm s}^{2}\eta \rho_{\star}|_{r_{\rm s}}
\tilde{v}_{w}^{2}}
 \left(\frac{1}{1+\frac{\kappa_0 T^{7/2}|_{r_{\rm s}}}{5 \rs
    \phi \rho c_s^3}}\right)
\nonumber \\ &\sim {\rm min}
  \begin{cases}
  20 \eta_{0.02}^{-1}
M_{\bullet,8}^{-0.8} v_{500}^{6.8} &  \text{unsaturated (core)}\\
 20 \eta_{0.02}^{-1}
M_{\bullet,8}^{-0.5} v_{500}^{5.4} &  \text{unsaturated (cusp)}\\
  2 \phi & \text{saturated},
  \end{cases}
 \label{eq:conduction}
\end{align}
where the second equality makes use of equations (\ref{eq:Tanalytic}),
(\ref{eq:stag_simple}), and we have approximated $\nabla^{2} \sim
1/r_{\rm s}^{2}$, $\nabla \sim 1/r_{\rm s}$.  We have approximated the
stellar density profile as (eq.~[\ref{eq:rhostar}])
\begin{eqnarray}
  \rho_{\star}|_{r_{\rm s}} &\simeq& \frac{M_{\bullet}(2-\Gamma)}{4\pi r_{\rm soi}^{3}}\left(\frac{r_{\rm s}}{r_{\rm soi}}\right)^{-1-\Gamma} \nonumber \\
 &\approx& \begin{cases}
    6.1 \times 10^{-19}M_{\bullet,8}^{-1.2}v_{500}^{2.2}\,{\rm g\,cm^{-3}}
    & \text{core} \\
    2.1 \times 10^{-18} M_{\bullet,8}^{-1.5}v_{500}^{3.6}
    \,{\rm g\,cm^{-3}}  & \text{cusp}, 
  \end{cases}
  \label{eq:rhostarrs}
\end{eqnarray}
where the stagnation radius is assume to reside well inside the Nuker
break radius.  Equation (\ref{eq:conduction}) shows that even in the
case of saturated conduction, the neglect of heat conduction results
in at most an order unity correction for expected values of the
saturation parameter $\phi < 0.1$, justifying its neglect in our
analysis.  Numerical experiments including conductivity confirm this
($\S\ref{sec:numerical}$). {\bf AG: If we make this statement then we
  should be sure to include the numerical experiments. The original
  formula was not correct for the saturated case. The numerical values
also changed somewhat. I would appreciate it if someone could double
check this. Also note that there is a weak core/cusp dependence in the
saturated case which I have chosen not to include.}

@@

Figure~\ref{fig:stag} shows our results for the stagnation radius
$r_{\rm s}$, expressed in ratio to sphere of influence radius $r_{\rm
  soi}$, with different colors showing different values of $v_{w}$.
Cusp and core galaxies are marked with square and triangles,
respectively.  Shown for comparison are our analytic results
(eq.~[\ref{eq:rs2main}]) with solid and dashed lines for cusp and core
galaxies, respectively, calculated assuming $\densSlope = 1$ and
$\densSlope= 0.6$, respectively.  Our analytic estimates are found to
provide accurate fits to the numerical results for $v_{\rm w} \gtrsim
\sigma$, but the assumptions leading to these estimates become invalid
for low $v_{\rm w}$ as the stagnation radius diverges to large radii.
For $v_{w} \gg \sigma$ the ratio $\rs/\rsoi$ does not depend
sensitively on break radius $r_{b}$, but the latter has a greater
influence when $v_{w} \lesssim \sigma$.  The three green squares which
are vertically aligned at the same value of $v_{w}/\sigma$ (close to
where the analytic estimate diverges) correspond to models with the
same black hole mass ($\Mbh = 10^7 \Msun$) and heating rate ($v_w =
300$ km s$^{-1}$) but different values of the break radius: $r_{b} = $
50, 100, and 400 pc (from top to bottom).  As $r_{\rm b} \rightarrow
r_{s}$, the effects of the break radius is to the push the stagnation
radius inwards, decreasing the SMBH accretion rate.

@@

@@

In Appendix \ref{app:windheat} we calculate the wind heating rate from
stellar winds, $v_{\rm w}^{\star}$, and the mass loss parameter,
$\eta$ (eq.~[\ref{eq:q}]), as a function of age, $\tau_{\star}$, of a
stellar population which is formed impulsively (Fig.~\ref{fig:vwImp}).  
At the earliest times ($\tau_{\star} \lesssim 10^{7}$ yr), the wind
heating rate exceeds 1000 km s$^{-1}$, while much later ($\tau_{\star}
\sim t_{\rm h}$) stellar wind heating dominated by main sequence winds
is much lower, $v^{\star}_{\rm w} \sim 50-100 $ km s$^{-1}$.  We show
in $\S\ref{sec:combined}$ that for the case of quasi-continueous star
formation representative of the average star formation history of loss
mass galaxies, the stellar wind heating rate produced by stellar winds
can also be significant, $v_{\rm w}^{\star} \sim 1000$ km s$^{-1}$.  
Stellar winds thus contribute a potentially important source of both
energy and mass for the CNM.  An additional uncertainty in the stellar wind heating rate results from the uncertain thermalization efficiency of massive stellar winds.  We assume this efficiency to be unity, and assumption that is at least partially offset by our conservative assumption of neglecting energy input from core collapse supernovae, which contribute a comparable energy injection rate to massive stellar winds.

@@

The SN Ia rate, $\RateIa$, depends on the age of the stellar population, as it represent the convolution of the star formation rate and the Ia delay time distribution (DTD) divided by the present stellar mass.  In
the limit of impulsive star formation, $\RateIa$ is the DTD evaluated at the time since the star formation episode.  The observationally-inferred DTD (Fig. 1 of \citealt{MaozMannucci+:2012a}) has the
approximate functional form \begin{align}
  R_{\rm Ia} =1.7\times 10^{-14}\left(\tau_{\star}/t_{\rm
      h}\right)^{-1.12} M_{\odot}^{-1}\,{\rm yr^{-1}}
\label{eq:DTD}
  \end{align}
  where $\tau_{\star}$ is the time since star formation
  (c.f.~\citealt{Scannapieco&Bildsten05}).

@@

\begin{align}
  \left.\frac{r_{\rm Ia}}{r_{\rm s}}\right|_{\rm v_{w}^{\rm Ia}}&\approx
  \begin{cases}
    8\, \eta_{0.02}^{-1} M_{\bullet,8}^{-1.1}(\epsilon_{\rm
     Ia}/0.4) (\tau_{\star}/t_{\rm h})^{-0.56}  & {\rm core}\\
    17\, \eta_{0.02}^{-1} M_{\bullet,8}^{-1.1}(\epsilon_{\rm
     Ia}/0.4) (\tau_{\star}/t_{\rm h})^{-0.56} &{\rm cusp}\\
   \end{cases} \nonumber\\
 &\approx 
 \begin{cases}
    8\, \eta_{0.02}^{-1} M_{\bullet,8}^{-1.1}(\epsilon_{\rm
     Ia}/0.4) (\tau_{\star}/t_{\rm h})^{0.74}  & {\rm core}\\
    17\, \eta_{0.02}^{-1} M_{\bullet,8}^{-1.1}(\epsilon_{\rm
     Ia}/0.4) (\tau_{\star}/t_{\rm h})^{0.74} &{\rm cusp}\\
   \end{cases}
\label{eq:rIars}
\end{align}
If $r_{\rm Ia} \gg r_{\rm s}$, then Ia heating can only be
approximated as a steady heating source near the stagnation radius for
extremely massive SMBHs with $M_{\bullet} \gtrsim 10^9 \Msun$ or in
the case of a very young stellar population ($\tau_{\star} \ll t_{\rm
h}$).

@@

The importance of Compton heating can be estimated by assuming the SMBH
radiates with a luminosity $L = \epsilon_{\rm rad} \dot{M}c^{2}$, where
$\epsilon_{\rm rad}$ is the radiative efficiency and where $\dot{M}$ is
estimated from equation (\ref{eq:mdot_analytic}).  Then using
equations (\ref{eq:rs_simple}), (\ref{eq:mdot_analytic}),
(\ref{eq:rhors}), (\ref{eq:rhostarrs}) we calculate that from equation
(\ref{eq:vw_eff}) that the effective heating rate at the stagnation radius is given by
\begin{align} v_{w}^{\rm C} \simeq
  \begin{cases} 27 \eta_{0.02}^{0.5}T_{\rm
C,9}^{0.5}\epsilon_{-2}^{0.5} M_{\bullet,8}^{0.38}v_{500}^{-1.4}\,{\rm
km\,s^{-1}} &, \text{core}\\ 30 \eta_{0.02}^{0.5}T_{\rm
C,9}^{0.5}\epsilon_{-2}^{0.5} M_{\bullet,8}^{0.24}v_{500}^{-0.7}\,{\rm
km\,s^{-1}} &, \text{cusp},
  \end{cases}
  \label{eq:vC}
\end{align} where $T_{C,9} = T_{C}/10^{9}$ K and $\epsilon_{-2} =
\epsilon_{\rm rad}/0.01 \sim 1$ is the maximum radiative efficiency
for an advective accretion flow expected to produce high $T_{\rm C}$
emission (e.g.~\citealt{Narayan&Yi95}).  We caveat that, unlike
stellar wind heating, Compton heating depends on radius, scaling as
$v_{w}^{\rm C}(r) \propto (n^{2}\xi/\rho_{\star})^{1/2} \propto
r^{(\Gamma-\densSlope-1)/2}$, i.e. $\propto r^{-0.6}$ and $\propto r^{-0.75}$
for core ($\Gamma = 0.8$; $\densSlope \simeq 1$) and cusp ($\Gamma = 0.1$;
$\densSlope \simeq 0.6$) galaxies, respectively.  The assumption of our model that the heating
parameter be constant with radius is not satisfied, but this radial
variation is sufficiently weak that it should not significantly alter
our conclusions.

If Compton heating acts alone, i.e. $\tilde{v}_{w} = v_{w}^{C}$, then solving equation
(\ref{eq:vC}) for $\tilde{v}_{\rm w}$ yields
\begin{align} v_{w}^{\rm C} \simeq
  \begin{cases} 150 \eta_{0.02}^{0.21}T_{\rm
C,9}^{0.21}\epsilon_{-2}^{0.21} M_{\bullet,8}^{0.16}\,{\rm km\,s^{-1}}
&, \text{core}\\ 96 \eta_{0.02}^{0.29}T_{\rm
C,9}^{0.29}\epsilon_{-2}^{0.29} M_{\bullet,8}^{0.14}\,{\rm km\,s^{-1}}
&, \text{cusp},
  \end{cases}
  \label{eq:vC2}
\end{align} 
Compton heating can thus be significant in young stellar populations with relatively high mass loss rates, e.g. $v_{w}^{\rm C} \gtrsim 300$ km s$^{-1}$ for $\eta \gtrsim 1$.  The mass accretion rate corresponding to the state where Compton heating limits the average accretion rate is given by substituting equation (\ref{eq:vC2}) into equation (\ref{eq:eddr_analytic}):
\begin{align}
\frac{\dot{M}_{C}}{\dot{M}_{\rm edd}} \approx 
\begin{cases} 3\times 10^{-3} \eta_{0.02}^{0.20}T_{\rm
C,9}^{-0.8}\epsilon_{-2}^{-0.8} M_{\bullet,8}^{0.15}
&, \text{core}\\ 8\times 10^{-4} \eta_{0.02}^{0.30}T_{\rm
C,9}^{-0.7}\epsilon_{-2}^{-0.7} M_{\bullet,8}^{0.14}
&, \text{cusp},
  \end{cases}
  \label{eq:MdotCa}
\end{align}
If the accretion luminosity $\epsilon = 0.1 \dot{M}/\dot{M}_{\rm edd}$ depends on the Eddington ratio as predicted by some models for radiatively inefficient accretion flows (\citealt{Narayan&Yi95}; \citealt{Narayan+98}), then the Compton-limited accretion rate becomes
\begin{align}
\frac{\dot{M}_{C}}{\dot{M}_{\rm edd}} \approx 
\begin{cases} 1.4\times 10^{-2} \eta_{0.02}^{0.11}T_{\rm
C,9}^{-0.44}M_{\bullet,8}^{0.08}
&, \text{core}\\ 6\times 10^{-3} \eta_{0.02}^{0.18}T_{\rm
C,9}^{-0.4} M_{\bullet,8}^{0.08}
&, \text{cusp}.
  \end{cases}
  \label{eq:MdotC}
\end{align}
{\bf AG: Note that I have included the bolometric correction for now.}

@@

As in the case of Compton heating, kinetic heating could in principle  `self-regulate' the accretion flow insofar as a lower heating rate results in a higher accretion rate (eq.~[\ref{eq:vjet}]), which in turn may create stronger jet feedback.  However, as it is not possible to make concrete predictions for such a process given the uncertainty in the efficiency of jet heating, we defer a more detailed discussion of the possible role of kinetic feedback to $\S\ref{sec:heating}$.

@@

\begin{figure}
\includegraphics[width=\columnwidth]{vwSources.pdf}
\caption{\label{fig:vwSources} {\it Top Panel:} Sources contributing
  to the total heating rate of the CNM, $\vwO$ ({\it black}),
  including stellar wind heating ({\it orange}), Ia supernovae ({\it
    green}), millisecond pulsars ({\it blue}), and compton heating
  ({\it pink}).  Each heating source varies with black hole mass
  $\Mbh$ calculated for average star formation histories from
  \citet{MosterNaab+:2013a} (see Appendix~\ref{app:windheat} for
  details).  {\it Middle Panel:} The ratio of the total heating rate
  ($\dot{q}_{\rm heat} \propto v_{w}^{2}$) from the top panel to the
  radiating cooling rate ($|\dot{q}_{\rm rad}|$) at the stagnation
  radius. {\it Bottom panel} Parameter $\eta$ characterizing stellar
  mass loss rate (eq.~[\ref{eq:q}]) as a function of black hole mass
  $\Mbh$, calculated for average star formation histories from and the
  ratio of Ia radius to stagnation radius as a function of $\Mbh$.
  The Ia radius calculated from equation~\eqref{eq:rIa} based on
  convolving the average star formation histories with the SN Ia DTD.
  The stagnation radius is calculated from \eqref{eq:stag_simple}
  using the total heating rate for each $\Mbh$ shown in the top panel
  assuming a cusp galaxy ($\Gamma=0.8$).}
\end{figure}

@@

The total gas heating rate, 
\begin{equation}
\vwO = \sqrt{(v_{w}^{\star})^{2} + (v_{w}^{\rm MSP})^{2} + (v_{w}^{\rm Ia})^{2} + (v_{w}^{\bullet})^{2}},
\label{eq:vtot}
\end{equation}
includes contributions from stellar winds, supernovae, pulsars, and radiative SMBH feedback (we neglect kinetic SMBH feedback for the moment, given its uncertain efficacy).  The strength of each heating source depends explicitly on the SMBH mass and the stellar population in the galactic nuclear region.  The latter could best be described by a single star burst formation in the past, or by a more continuous star formation history that itself varies systematically with the galaxy mass and hence $\Mbh$.

@@

{\bf NCS: is this reduced heating rate thermally unstable under
  Aleksey's revised formula?  We should comment. AG: What revised
  formula.}

% However, if Ia supernovae are included in the schematic way described
% above, the flow again becomes thermally stable for $\Mbh \gtrsim
% XXXX$.

>>>>

\begin{table*}
\begin{threeparttable}
%\centering
\begin{minipage}{18cm}
\caption{Definitions of commonly used variables}
\begin{tabular}{ll}
\hline
{Variable} & {Definition} \\
\hline
$M_{\bullet}$ & Black hole mass \\
$\tilde{v}_{w}$ & Total heating parameter, including minimum heating rate from stellar velocity dispersion \\
$v_{w}$ & Total heating parameter, excluding heating rate from stellar velocity dispersion \\
$r_{s}$ & Stagnation radius (where radial velocity goes to zero) \\
$r_{\rm soi}$ & radius of sphere of influence (eq.~[\ref{eq:rsoi}]) \\
$r_{\rm b}$ & outer break radius of stellar density profile \\ 
$r_{\rm Ia}$ & radius exterior to which Ia SN are infrequent compared to the dynamical/inflow timescale (eq.~[\ref{eq:rIa}]) \\ 
$\rho_{\star}(r)$ & 3D radial stellar density profile \\
$\rho(r)$ & gas density of CNM \\
$M_{\star}(r)$ & total enclosed stellar mass inside radius $r$ \\
$M_{\rm enc}(r)$ & total encolsed mass inside radius $r$ (SMBH + stars) \\
$q(r)$ & mass source term due to stellar winds (eq.~[\ref{eq:q}]) \\
$\eta$ & parameter setting normalization of mass input from stellar winds (eq.~[\ref{eq:q}]) \\
$\tau_{\star}$ & age of stellar population, in case of a single burst of star formation \\
$\Gamma$ & power-law slope of radial stellar density profile interior to the break radius \\
$\sigma(r)$ & stellar velocity dispersion \\
$\dot{M}$ & mass accretion rate \\
$\dot{M}_{\rm Ia}$ & maximum mass accretion rate as limited by SN Ia blow-out (eq.~[\ref{eq:eddr_Ia}]) \\
$\dot{M}_{\rm C}$ & equilibrium accretion rate set by Compton heating (eq.~[\ref{eq:MdotC}]) \\
$\dot{M}_{\rm TI}$ & maximum accretion rate for thermally stable accretion (eq.~[\ref{eq:Mdotmax}]) \\
$\dot{q}_{\rm heat}/|\dot{q}_{\rm rad}|$ & ratio of external heating (stellar winds, SN Ia, MSPs) to radiative cooling (eq.~[\ref{eq:cooling2}]) \\
$t_{\rm h}$ & Hubble timescale \\
$\nu$ & gas density power-law slope at the stagnation radius (eq.~[\ref{eq:densSlope}]) \\
\hline
\label{table:definitions}  
\end{tabular}
\begin{tablenotes}
\item{$^{(a)}FILL IN$}
\end{tablenotes}
\end{minipage}
\end{threeparttable}

@@

Our analytic derviations neglect the effects of heat conduction, an assumption we now check.  The ratio of the magnitude of the conductive heating rate (eq.~[\ref{eq:qdotcond}]) to the external heating rate at the stagnation radius is given by
\begin{align}
  \left.\frac{\nabla\cdot(\kappa \nabla T)}{q v_{\rm
w}^{2}/2}\right|_{r_{\rm s}} &\sim \frac{2t_{\rm h}\kappa_0
T|_{r_{\rm s}}^{7/2}}{r_{\rm s}^{2}\eta \rho_{\star}|_{r_{\rm s}}
\tilde{v}_{w}^{2}}
 \left(\frac{1}{1+\frac{\kappa_0 T^{7/2}|_{r_{\rm s}}}{5 \rs
    \phi \rho c_s^3}}\right)
\nonumber \\ &\sim {\rm min}
  \begin{cases}
  20 \eta_{0.02}^{-1}
M_{\bullet,8}^{-0.8} v_{500}^{6.8} &  \text{unsaturated (core)}\\
 20 \eta_{0.02}^{-1}
M_{\bullet,8}^{-0.5} v_{500}^{5.4} &  \text{unsaturated (cusp)}\\
  2 \phi & \text{saturated},
  \end{cases}
 \label{eq:conduction}
\end{align}
where the second equality makes use of equations (\ref{eq:Tanalytic}),
(\ref{eq:stag_simple}), and we have approximated $\nabla^{2} \sim
1/r_{\rm s}^{2}$, $\nabla \sim 1/r_{\rm s}$.  We have approximated the
stellar density profile as (eq.~[\ref{eq:rhostar}])
\begin{eqnarray}
  \rho_{\star}|_{r_{\rm s}} &\simeq& \frac{M_{\bullet}(2-\Gamma)}{4\pi r_{\rm soi}^{3}}\left(\frac{r_{\rm s}}{r_{\rm soi}}\right)^{-1-\Gamma} \nonumber \\
 &\approx& \begin{cases}
    6.1 \times 10^{-19}M_{\bullet,8}^{-1.2}v_{500}^{2.2}\,{\rm g\,cm^{-3}}
    & \text{core} \\
    2.1 \times 10^{-18} M_{\bullet,8}^{-1.5}v_{500}^{3.6}
    \,{\rm g\,cm^{-3}}  & \text{cusp}, 
  \end{cases}
  \label{eq:rhostarrs}
\end{eqnarray}
where the stagnation radius is assume to reside well inside the Nuker
break radius and for clarity we have not distinguished between cusp and core galaxies.  Equation (\ref{eq:conduction}) shows that even in the
case of saturated conduction, the neglect of heat conduction results
in at most an order unity correction for expected values of the
saturation parameter $\phi < 0.1$, justifying its neglect in our
analysis.  Numerical experiments including conductivity confirm this
($\S\ref{sec:numerical}$).

@@

Figure~\ref{fig:stag} shows our results for the stagnation radius
$r_{\rm s}$, expressed in ratio to sphere of influence radius $r_{\rm
  soi}$, with different colors showing different values of $v_{w}$.
Cusp and core galaxies are marked with square and triangles,
respectively.  Shown for comparison are our analytic results
(eq.~[\ref{eq:rs2main}]) with solid and dashed lines for cusp and core
galaxies, respectively, calculated assuming $\densSlope = 1$ and
$\densSlope= 0.6$, respectively (eq.~[\ref{eq:densSlope}]).  Our analytic estimates are found to
provide accurate fits to the numerical results for $v_{\rm w} \gtrsim
\sigma$, but the assumptions leading to these estimates become invalid
for low $v_{\rm w}$ as the stagnation radius diverges to large radii.
For $v_{w} \gg \sigma$ the ratio $\rs/\rsoi$ does not depend
sensitively on break radius $r_{b}$, but the latter has a greater
influence when $v_{w} \lesssim \sigma$.  The three green squares which
are vertically aligned at the same value of $v_{w}/\sigma$ (close to
where the analytic estimate diverges) correspond to models with the
same black hole mass ($\Mbh = 10^7 \Msun$) and heating rate ($v_w =
300$ km s$^{-1}$) but different values of the break radius: $r_{b} = $
50, 100, and 400 pc (from top to bottom).  As $r_{\rm b} \rightarrow
r_{s}$, the effects of the break radius is to the push the stagnation
radius inwards, decreasing the SMBH accretion rate.

@@

In addition to our standard set of solutions neglecting thermal conduction and cooling, we explore a few test simulations including these effects, as marked in Table \ref{table:models}.  {\bf BDM: EXPAND!!!!  Explain that they don't matter.}

@@

In Appendix \ref{app:windheat} we calculate the wind heating rate from
stellar winds, $v_{\rm w}^{\star}$, and the mass loss parameter,
$\eta$ (eq.~[\ref{eq:q}]), as a function of age, $\tau_{\star}$, of a
stellar population which is formed impulsively (Fig.~\ref{fig:vwImp}).  
At the earliest times ($\tau_{\star} \lesssim 10^{7}$ yr), the wind
heating rate exceeds 1000 km s$^{-1}$, while much later ($\tau_{\star}
\sim t_{\rm h}$) stellar wind heating dominated by main sequence winds
is much lower, $v^{\star}_{\rm w} \sim 50-100 $ km s$^{-1}$.  We show
in $\S\ref{sec:combined}$ that for the case of quasi-continueous star
formation representative of the average star formation history of loss
mass galaxies, the stellar wind heating rate produced by stellar winds
can also be significant, $v_{\rm w}^{\star} \sim 1000$ km s$^{-1}$.  
Stellar winds thus contribute a potentially important source of both
energy and mass for the CNM.  An additional uncertainty in the stellar wind heating rate results from the uncertain thermalization efficiency of massive stellar winds.  We assume this efficiency to be unity, an optimistic assumption which is offset by our neglect of energy input from core collapse supernovae, which contribute an energy comparable to that from massive stellar winds.

@@

The SN Ia rate, $\RateIa$, depends on the age of the stellar population, as it represent the convolution of the star formation rate and the Ia delay time distribution (DTD) divided by the present stellar mass.  In
the limit of impulsive star formation, $\RateIa$ is the DTD evaluated at the time since the star formation episode.  The observationally-inferred DTD (Fig. 1 of \citealt{MaozMannucci+:2012a}) has the
approximate functional form \begin{align}
  R_{\rm Ia} =1.7\times 10^{-14}\left(\tau_{\star}/t_{\rm
      h}\right)^{-1.12} M_{\odot}^{-1}\,{\rm yr^{-1}}
\label{eq:DTD}
  \end{align}
  where $\tau_{\star}$ is the time since star formation.

@@

\begin{align}
  \left.\frac{r_{\rm Ia}}{r_{\rm s}}\right|_{\rm v_{w}^{\rm Ia}}&\approx
  \begin{cases}
    8\, \eta_{0.02}^{-1} M_{\bullet,8}^{-1.1}(\epsilon_{\rm
     Ia}/0.4) (\tau_{\star}/t_{\rm h})^{-0.56}  & {\rm core}\\
    17\, \eta_{0.02}^{-1} M_{\bullet,8}^{-1.1}(\epsilon_{\rm
     Ia}/0.4) (\tau_{\star}/t_{\rm h})^{-0.56} &{\rm cusp}\\
   \end{cases} \nonumber\\
 &\approx 
 \begin{cases}
    8\, M_{\bullet,8}^{-1.1}(\epsilon_{\rm
     Ia}/0.4) (\tau_{\star}/t_{\rm h})^{0.74}  & {\rm core}\\
    17\, M_{\bullet,8}^{-1.1}(\epsilon_{\rm
     Ia}/0.4) (\tau_{\star}/t_{\rm h})^{0.74} &{\rm cusp}\\
   \end{cases}
\label{eq:rIars}
\end{align}
If $r_{\rm Ia} \gg r_{\rm s}$, then SN Ia heating can only be
approximated as a steady heating source near the stagnation radius for
extremely massive SMBHs with $M_{\bullet} \gtrsim 10^9 \Msun$ or in
the case of a very young stellar population ($\tau_{\star} \ll t_{\rm
h}$).

@@

The importance of Compton heating can be estimated by assuming the SMBH
radiates with a luminosity $L = \epsilon_{\rm rad} \dot{M}c^{2}$, where
$\epsilon_{\rm rad}$ is the radiative efficiency and where $\dot{M}$ is
estimated from equation (\ref{eq:mdot_analytic}).  Then using
equations (\ref{eq:rs_simple}), (\ref{eq:mdot_analytic}),
(\ref{eq:rhors}), (\ref{eq:rhostarrs}) we calculate that from equation
(\ref{eq:vw_eff}) that the effective heating rate at the stagnation radius is given by
\begin{align} v_{w}^{\rm C} \simeq
  \begin{cases} 27 \eta_{0.02}^{0.5}T_{\rm
C,9}^{0.5}\epsilon_{-2}^{0.5} M_{\bullet,8}^{0.38}v_{500}^{-1.4}\,{\rm
km\,s^{-1}} &, \text{core}\\ 30 \eta_{0.02}^{0.5}T_{\rm
C,9}^{0.5}\epsilon_{-2}^{0.5} M_{\bullet,8}^{0.24}v_{500}^{-0.7}\,{\rm
km\,s^{-1}} &, \text{cusp},
  \end{cases}
  \label{eq:vC}
\end{align} where $T_{C,9} = T_{C}/10^{9}$ K and $\epsilon_{-2} =
\epsilon_{\rm rad}/0.01 \sim 1$ is the maximum radiative efficiency
for an advective accretion flow expected to produce high $T_{\rm C}$
emission (e.g.~\citealt{Narayan&Yi95}).  We caveat that, unlike
stellar wind heating, Compton heating depends on radius, scaling as
$v_{w}^{\rm C}(r) \propto (n^{2}\xi/\rho_{\star})^{1/2} \propto
r^{(\Gamma-\densSlope-1)/2}$, i.e. $\propto r^{-0.6}$ and $\propto r^{-0.75}$
for core ($\Gamma = 0.8$; $\densSlope \simeq 1$) and cusp ($\Gamma = 0.1$;
$\densSlope \simeq 0.6$) galaxies, respectively.  Our model's assumption that the heating
parameter be radially constant is not satisfied, but this variation is sufficiently weak that it should not significantly alter
our conclusions.

If Compton heating acts alone, i.e. $\tilde{v}_{w} = v_{w}^{C}$, then solving equation
(\ref{eq:vC}) for $\tilde{v}_{\rm w}$ yields
\begin{align} v_{w}^{\rm C} \simeq
  \begin{cases} 150 \eta_{0.02}^{0.21}T_{\rm
C,9}^{0.21}\epsilon_{-2}^{0.21} M_{\bullet,8}^{0.16}\,{\rm km\,s^{-1}}
&, \text{core}\\ 96 \eta_{0.02}^{0.29}T_{\rm
C,9}^{0.29}\epsilon_{-2}^{0.29} M_{\bullet,8}^{0.14}\,{\rm km\,s^{-1}}
&, \text{cusp},
  \end{cases}
  \label{eq:vC2}
\end{align} 
Compton heating can thus be significant in young stellar populations with relatively high mass loss rates, e.g. $v_{w}^{\rm C} \gtrsim 300$ km s$^{-1}$ for $\eta \gtrsim 1$.  The mass accretion rate corresponding to the state where Compton heating limits the average accretion rate is given by substituting equation (\ref{eq:vC2}) into equation (\ref{eq:eddr_analytic}):
\begin{align}
\frac{\dot{M}_{C}}{\dot{M}_{\rm edd}} \approx 
\begin{cases} 3\times 10^{-3} \eta_{0.02}^{0.20}T_{\rm
C,9}^{-0.8}\epsilon_{-2}^{-0.8} M_{\bullet,8}^{0.15}
&, \text{core}\\ 8\times 10^{-4} \eta_{0.02}^{0.30}T_{\rm
C,9}^{-0.7}\epsilon_{-2}^{-0.7} M_{\bullet,8}^{0.14}
&, \text{cusp},
  \end{cases}
  \label{eq:MdotCa}
\end{align}
If the accretion luminosity $\epsilon = 0.1 \dot{M}/\dot{M}_{\rm edd}$ depends on the Eddington ratio as predicted by some models for radiatively inefficient accretion flows (\citealt{Narayan&Yi95}; \citealt{Narayan+98}), then the Compton-limited accretion rate becomes
\begin{align}
\frac{\dot{M}_{C}}{\dot{M}_{\rm edd}} \approx 
\begin{cases} 1.4\times 10^{-2} \eta_{0.02}^{0.11}T_{\rm
C,9}^{-0.44}M_{\bullet,8}^{0.08}
&, \text{core}\\ 6\times 10^{-3} \eta_{0.02}^{0.18}T_{\rm
C,9}^{-0.4} M_{\bullet,8}^{0.08}
&, \text{cusp}.
  \end{cases}
  \label{eq:MdotC}
\end{align}
{\bf AG: Note that I have included the bolometric correction for now.  BDM: are you doing everything consistently?}

@@

As in the case of Compton heating, kinetic heating could in principle  `self-regulate' the accretion flow insofar as a lower heating rate results in a higher accretion rate (eq.~[\ref{eq:vjet}]), which in turn may create stronger jet feedback.  However, as it is not possible to make concrete predictions for such a process given the uncertainty in the efficiency of jet heating (see $\S\ref{sec:heating}$ for further discussion).

@@

\begin{figure}
\includegraphics[width=\columnwidth]{vwSources.pdf}
\caption{\label{fig:vwSources} {\it Top Panel:} Sources contributing
  to the total heating rate of the CNM, $\vwO$ ({\it black}),
  including stellar wind heating ({\it orange}), Ia supernovae ({\it
    green}), millisecond pulsars ({\it blue}), and compton heating
  ({\it pink}).  Each heating source varies with black hole mass
  $\Mbh$ calculated for average star formation histories from
  \citet{MosterNaab+:2013a} (see Appendix~\ref{app:windheat} for
  details).  {\it Middle Panel:} The ratio of the total heating rate
  ($\dot{q}_{\rm heat} \propto v_{w}^{2}$) from the top panel to the
  radiating cooling rate ($|\dot{q}_{\rm rad}|$) at the stagnation
  radius. {\it Bottom panel} Parameter $\eta$ characterizing stellar
  mass loss rate (eq.~[\ref{eq:q}]) as a function of black hole mass
  $\Mbh$, calculated for average star formation histories from and the
  ratio of Ia radius to stagnation radius as a function of $\Mbh$.}
  %The Ia radius calculated from equation~\eqref{eq:rIa} based on
  %convolving the average star formation histories with the SN Ia DTD.
  %The stagnation radius is calculated from \eqref{eq:stag_simple}
  %using the total heating rate for each $\Mbh$ shown in the top panel
  %assuming a cusp galaxy ($\Gamma=0.8$).}
\end{figure}

@@

The total gas heating rate, 
\begin{equation}
\vwO = \sqrt{(v_{w}^{\star})^{2} + (v_{w}^{\rm MSP})^{2} + (v_{w}^{\rm Ia})^{2} + (v_{w}^{\bullet})^{2}},
\label{eq:vtot}
\end{equation}
includes contributions from stellar winds, supernovae, pulsars, and radiative SMBH feedback.  The strength of each heating source depends explicitly on the SMBH mass and the stellar population in the galactic nuclear region.  The latter could best be described by a single star burst formation in the past, or by a more continuous star formation history that itself varies systematically with the galaxy mass and hence $\Mbh$.

@@
